% Resumo em língua estrangeira (em inglês Abstract, em espanhol Resumen, em francês Résumé)
\begin{center}
	{\Large{\textbf{\ForeignTitle}}}
\end{center}

\vspace{1cm}

\begin{flushright}
	Author: \Author\\
	Advisor: \Advisor\\
	%Co-advisor: \Coadvisor
\end{flushright}

\vspace{1cm}

\begin{center}
	\Large{\textsc{\textbf{Abstract}}}
\end{center}

\noindent Real-time strategy (RTS) games hold many challenges in the creation of a game artificial intelligence (AI). One of those challenges is creating an effective plan for a given context. A game used as platform for experiments and competition of game AIs is StarCraft. Its game AIs have struggled to adapt and create good plans to counter the opponent strategy. In this paper, a new scheduling model is proposed to planning problems on RTS games. This model considers cyclic events and consists in solving a multi-objective problem that satisfies constraints imposed by the game. Resources, tasks and cyclic events that translate the game into an instance of the problem are considered. The initial state contains information about resources, uncompleted tasks and on-going events. The strategy defines which resources to maximize or minimize and which constraints are applied to the resources, as well as to the project horizon. Four multi-objective optimizers are investigated: NSGA-II and its knee variant, GRASP and Ant Colony. Experiments with cases based on real Starcraft problems are reported. In these experiments, NSGA-II showed better performance than the other optimizers.

\noindent\textit{Keywords}: Optimization Model, Multi-objective Optimization, Real-time Strategy Games, Project Scheduling.